---
title: "Archaeopteryx"
author: "zach cp"
date: "5/5/2017"
output: html_document
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```


The goal of archaeopteryx is to wrap the wonderful [archaeopteryx.js](https://sites.google.com/site/cmzmasek/home/software/archaeopteryx-js) library and make it accessible as an htmlwidget. Currently the basics work but I will be exploring changes to the API to try to make it work with R's pipe-based workflow.

## Install

```{r, eval=FALSE}
require(devtools)
devtools::install_github("zachcp/archaeopteryx-js")
```

## Mini Roadmap

A few thoughts on how to improve this code (no guarantees):

- To be able to get all of the control-elements, we will need to specify the DOM elements.
- If we want to have multiple trees on an RMD page, the DOM elements need to be labelled in the RMB code using htmlwidget tags.
- To do this is not-trivial since the code names are hardcoded in the archaeopteryx.js code and at first look they do not seem to be replaces usign the `options` or `settings` features that allow you to customize the chart.
- provide access to some reasonably complete set of options that can be passed to users.
- right now newick strings are passed/parsed. Can a direct JSON blob be transfered in order to save the encode/decode step? This would also allow us to adorn information on each node.
- be able to specify per-node attributes - which measn being able to pass in the information and using an API to modify the nodes.


## Simple Usage.


```{r, warning=FALSE, message=FALSE}
## basic example code
library(archaeopteryx)
library(ape)
library(data.table)
library(Biostrings)

tree <- ape::read.tree(text="(mammal,(turtle,rayfinfish,(frog,salamander)));")
dna1 <- DNAStringSet(c("AAA","CCC","TTT","TTG","GTG"))
names(dna1) <- c("mammal", "turtle", "rayfinfish", "frog", "salamander")
phyJ <- create_phyloJ(phylo = tree, seqs = dna1)
phyJ <- add_sequences(phyJ)

archaeopteryx(phyJ)

```


# Color SubClades

```{r, warning=FALSE, message=FALSE}

t1   <- ape::read.tree(text="(mammal,(turtle,rayfinfish,(frog,salamander)));")
dt   <- data.table(nodes=c("mammal","turtle","rayfinfish","frog","salamander"), 
                   size=c(1,2,3,4,5),
                   scale = c("a","b","c","d","d"))

red      <- J("java.awt.Color")$RED
phyJ     <- create_phyloJ(phylo=t1, annotation=dt)
mrca     <- get_MRCA(phyJ, tips=c("frog", "turtle"))
set_clade_color(phyJ, mrca, red)
archaeopteryx(phyJ)

```


# Color Multiple SubClades

```{r, warning=FALSE, message=FALSE}

data(bird.families)
phyJ <- create_phyloJ(bird.families)
mrca1 <- get_MRCA(phyJ, c("Pardalotidae", "Centropidae"))
mrca2 <- get_MRCA(phyJ, c("Laridae", "Thinocoridae"))
red     <- J("java.awt.Color")$RED
blue    <- J("java.awt.Color")$BLUE
phyJ <- set_clade_color(phyJ, mrca1, red)
phyJ <- set_clade_color(phyJ, mrca2, blue)
archaeopteryx(phyJ)
```

